MCTS Applied to Co-operative Problems

### 2015-07-02 Report/ceec.tex

\subsection{AI Controllers}
\subsubsection{Random}
The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
\subsubsection{Keyboard}
The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
\subsubsection{\gls{mcts}}
The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border. No knowledge about the game is provided and the assumption is made that the other player will play randomly. The fixed rollout border makes a significant improvement in iterations per decision (On the machine from 1-3 to 500-600 in 40ms). This greatly improves the ability of \gls{mcts} to make informed decisions. The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
\subsubsection{A*}
An intelligent agent was required that could provide comparison to how the MCTS is performing. A Star was selected and written to view the problem as selecting the shortest path of actions that would result in reaching the goals.
\subsubsection{Macro Action Genetic Algorithm}
The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability.
\subsubsection{Variable Macro Action Genetic Algorithm}

\subsection{Methodology}
Initially, observations were made to see how \gls{mcts} handled the problem. At first, with a small computational budget it seemed like \gls{mcts} would perform poorly, with near random movement seeming to emerge.

@@

With this observation made - the computational budget was increased ten-fold, and the \gls{mcts} agents performed significantly better. Typical behaviour would be near optimal with significantly less random sections of movement. This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.
\bibliographystyle{IEEEtran}
\bibliography{ceec}

>>>>

\subsection{AI Controllers}
A small set of AI Controllers were created in order to attempt to solve the problem domain. None of the agents have the ability to communicate with another agent.
\subsubsection{Random}
The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
\subsubsection{Keyboard}
The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
\subsubsection{\gls{mcts}}
The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border. No knowledge about the game is provided and the assumption is made that the other player will play randomly. The fixed rollout border makes a significant improvement in iterations per decision (On the machine from 1-3 to 500-600 in 40ms). This greatly improves the ability of \gls{mcts} to make informed decisions. The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
\subsubsection{A*}
An intelligent agent was required that could provide comparison to how the MCTS is performing. A Star was selected and written to view the problem as selecting the shortest path of actions that would result in reaching the goals.
\subsubsection{Macro Action Genetic Algorithm}
The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability.
\subsubsection{Variable Macro Action Genetic Algorithm}

\subsection{Initial Testing}
Initially, observations were made to see how \gls{mcts} handled the problem. At first, with a small computational budget it seemed like \gls{mcts} would perform poorly, with near random movement seeming to emerge.

@@

With this observation made - the computational budget was increased ten-fold, and the \gls{mcts} agents performed significantly better. Typical behaviour would be near optimal with significantly less random sections of movement. This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.
\subsection{Tournament}
A round robin tournament with three maps and the assembled Agents with various parameters was run - allowing each Agent to be paired with every other Agent (including itself) and play the game ten times per level.
\bibliographystyle{IEEEtran}
\bibliography{ceec}
